---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# matrixmodp

<!-- badges: start -->
<!-- badges: end -->

The goal of matrixmodp is to make two matrix algebra tasks easier when working with the fields $\mathbb{F}_p$. Specifically, this package provides two functions: `rref_p()` calculates the reduced-row echelon form of a matrix, and `inv_p()` calculates the inverse of a (square, invertible) matrix.

## Installation

You can install the development version of matrixmodp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rhigginbottom/matrixmodp")
```

## Example

We first provide an example of finding the RREF of a matrix with entries in $\mathbb{F}_5$.

```{r example}
library(matrixmodp)
entries <- c(4, 1, 2, 0, 0, 3, 4, 0, 0, 1, 4, 1)
A <- matrix(entries, 3, 4)
rref_p(A, 5)
```

We now show how to find the inverse of a $3\times 3$ matrix over $\mathbb{F}_7$.

```{r}
library(matrixmodp)
entries <- c(3, 3, 3, 2, 0, 2, 1, 2, 5)
A <- matrix(entries, 3, 3)
inv_p(A, 7)
```

